\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-06-02 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex

Packages such as \texttt{doxywizard} can be used to visualize the
subroutine calling tree of the source code. \texttt{Doxywizard} is
a GUI front-end for configuring and running \texttt{doxygen}.

>>>>

\noindent
Packages such as \texttt{Doxywizard} can be used to visualize the calling tree of the
subroutines of the  source code. \texttt{Doxywizard} is
a GUI front-end for configuring and running \texttt{Doxygen}.

\bigskip

\noindent To do your own call graphs, you can follow these simple steps below.

\begin{enumerate}
\setcounter{enumi}{-1}
\item Install \texttt{Doxygen} \underline{and} \texttt{graphviz} (the two are usually in the package manager of classic Linux distribution).
\item Run in the terminal : \texttt{doxygen -g}, which creates a \texttt{Doxyfile} that tells doxygen what you want it to do.
\item Edit the Doxyfile. Two Doxyfile-type files have been already committed in the directory \\
\noindent \texttt{specfem3d/doc/Call\_trees}:

\begin{itemize}
\item[\textbullet] \texttt{Doxyfile\_truncated\_call\_tree} will generate call graphs with maximum 3 or 4 levels of tree structure,
\item[\textbullet] \texttt{Doxyfile\_complete\_call\_tree} will generate call graphs with complete tree structure.
\end{itemize}

The important entries in the Doxyfile are:

\begin{description}
\item [{\texttt{PROJECT\_NAME}}] 
\item [{\texttt{OPTIMIZE\_FOR\_FORTRAN}}] Set to YES
\item [{\texttt{EXTRACT\_ALL}}] Set to YES
\item [{\texttt{EXTRACT\_PRIVATE}}] Set to YES
\item [{\texttt{EXTRACT\_STATIC}}] Set to YES
\item [{\texttt{INPUT}}] From the directory \texttt{specfem3d/doc/Call\_trees}, it is \texttt{"../../src/"}
\item [{\texttt{FILE\_PATTERNS}}] In SPECFEM case, it is \texttt{*.f90* *.F90* *.c* *.cu* *.h*}
\item [{\texttt{HAVE\_DOT}}] Set to YES
\item [{\texttt{CALL\_GRAPH}}] Set to YES
\item [{\texttt{CALLER\_GRAPH}}] Set to YES
\item [{\texttt{DOT\_PATH}}] The path where is located the dot program graphviz (if it is not in your \$PATH)
\item [{\texttt{RECURSIVE}}] This tag can be used to turn specify whether or not subdirectories should be searched for input files as well. In the case of SPECFEM, set to YES.
\item [{\texttt{EXCLUDE}}] Here, you can exclude:  \\
\texttt{"../../src/specfem3D/older\_not\_maintained\_partial\_OpenMP\_port"}\\
\texttt{"../../src/decompose\_mesh/scotch"}\\
\texttt{"../../src/decompose\_mesh/scotch\_5.1.12b"}
\item [{\texttt{DOT\_GRAPH\_MAX\_NODES}}] to set the maximum number of nodes that will be shown in the graph. If the number of nodes in a graph becomes larger than this value, doxygen will truncate the graph, which is visualized by representing a node as a red box. Minimum value: 0, maximum value: 10000, default value: 50.
\item [{\texttt{MAX\_DOT\_GRAPH\_DEPTH}}] to set the maximum depth of the graphs generated by dot. A depth value of 3 means that only nodes reachable from the root by following a path via at most 3 edges will be shown. Using a depth of 0 means no depth restriction. Minimum value: 0, maximum value: 1000, default value: 0.

\item Run : \texttt{doxygen Doxyfile}, HTML and LaTeX files created by default in \texttt{html} and \texttt{latex} subdirectories.

\item To see the call trees, you have to open the file \texttt{html/index.html} in your \underline{browser}. You will have many informations about each subroutines of SPECFEM (not only call graphs), you can click on every boxes / subroutines. It show you the call, and, the caller graph of each subroutine : the subroutines called by the concerned subroutine, and the previous subroutines who call this subroutine (the previous path), respectively. In the case of a truncated calling tree, the boxes with a red border indicates a node that has \underline{more} arrows than are shown (in other words: the graph is truncated with respect to this node).

\end{enumerate}

\medskip

\noindent Finally, some useful links:

\begin{itemize}
\item[\textbullet] a good and short summary for the basic utilisation of Doxygen:

\texttt{http://www.softeng.rl.ac.uk/blog/2010/jan/30/callgraph-fortran-doxygen/} ,

\item[\textbullet] to configure the diagrams :

\texttt{http://www.stack.nl/~dimitri/doxygen/manual/diagrams.html} ,

\item[\textbullet] the complete alphabetical index of the tags in Doxyfile:

\texttt{http://www.stack.nl/~dimitri/doxygen/manual/config.html} ,

\item[\textbullet] more generally, the Doxygen manual:

\texttt{http://www.stack.nl/~dimitri/doxygen/manual/index.html} .

\end{itemize}

\medskip
